---
title: "Executive Summary Example"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
---

```{r, RSetup, include=FALSE}
library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(DT)
```

# Analysis Results {.storyboard data-icon='fa-bar-chart'}

### Static Graph 1

```{r, fig.width=12, fig.height=8}
ggplot(data = faithful,
       mapping = aes(x = waiting, y = eruptions, color = ..level..)) +
  geom_density2d(size = 1, linetype = 'dashed') +
  scale_x_continuous(name = 'Days between Eruptions') +
  scale_y_continuous(name = 'Geyser Eruption Size') +
  scale_color_viridis_c(option = 'plasma') +
  theme_classic() +
  theme(legend.position = 'none')
```

---

<span style='font-size: 16px; font-weight: bold;'>Commentary:</span>

This is the commentary for slide 1.

<hr><span style='font-size: 16px; font-weight: bold;'>Data:</span>

[Link to Data](#FaithfulTable)

### Static Graph 2

```{r, fig.width=12, fig.height=8}
ggplot(data = seals,
       mapping = aes(x = long,
                     xend = long + delta_long,
                     y = lat,
                     yend = lat + delta_lat,
                     color = sqrt((delta_long ^ 2) + (delta_lat ^ 2)))) +
  geom_segment(arrow = arrow(angle = 30, length = unit(x = .2, units = 'cm')),
               size = 1) +
  scale_y_continuous(name = 'Latitude') +
  scale_x_continuous(name = 'Longitude') +
  scale_color_viridis_c(trans = 'log') +
  theme_classic() +
  theme(legend.position = 'none')
```

---

<span style='font-size: 16px; font-weight: bold;'>Commentary:</span>

This is the commentary for slide 2.

<hr><span style='font-size: 16px; font-weight: bold;'>Data:</span>

[Link to Data](#SealTable)

### Interactive Graph 1

```{r, fig.width=12, fig.height=8}
ggplotly(ggplot(data = mpg,
                mapping = aes(x = class, y = hwy)) +
           geom_point(mapping = aes(color = hwy,
                                    text = str_c('Manufacturer: <b>', manufacturer, '</b>',
                                                 '\nModel: <b>', model, '</b>',
                                                 '\nClass: <i>', class, '</i>',
                                                 '\n\nHwy MPG: ', as.character(hwy),
                                                 '\nCity MPG: ', as.character(cty))),
                      position = position_jitter(width = .2, height = .4)) +
           scale_y_continuous(name = 'Car Hwy MPG') +
           scale_x_discrete(name = 'Car Class') +
           scale_color_viridis_c() +
           theme_classic() +
           theme(legend.position = 'none'),
         tooltip = 'text')
```

---

<span style='font-size: 16px; font-weight: bold;'>Commentary:</span>

This is the commentary for slide 3.

<hr><span style='font-size: 16px; font-weight: bold;'>Data:</span>

[Link to Data](#MPGTable)

### Interactive Graph 2

``` {r, fig.width=12, fig.height=8}
ggplotly(ggplot(data = mpg %>% group_by(manufacturer) %>% summarise(NModels = n()),
                mapping = aes(x = manufacturer, y = NModels, fill = NModels,
                              text = str_c('Manufacturer: <b>', manufacturer, '</b>',
                                           '\n# Car Models: ', as.character(NModels)))) +
           geom_col() +
           scale_x_discrete(name = 'Manufacturer') +
           scale_y_continuous(name = '# of Car Models') +
           scale_fill_viridis_c() +
           coord_flip() +
           theme_classic() +
           theme(legend.position = 'none'),
         tooltip = 'text')
```

---

<span style='font-size: 16px; font-weight: bold;'>Commentary:</span>

This is the commentary for slide 4.

<hr><span style='font-size: 16px; font-weight: bold;'>Data:</span>

[Link to Data](#MPGTable)

# Slide 1 Data (Geyser Eruption Time) {#FaithfulTable data-icon='fa-clock' data-navmenu='Tables'}

``` {r}
DT::datatable(data = faithful,
              colnames = c('Eruption Size', 'Days Between Eruptions'),
              filter = 'top',
              rownames = FALSE,
              extensions = 'Buttons',
              options = list(dom = 'Blfrtip',
                             buttons = c('csvHtml5', 'excelHtml5'),
                             pageLength = 10,
                             lengthMenu = c(10, 100, 1000)))
```

# Slide 2 Data (Seal Migrations) {#SealTable data-icon='fa-map-marker' data-navmenu='Tables'}

``` {r}
DT::datatable(data = seals,
              colnames = c('Latitude', 'Longitude', 'Longitude Movement', 'Latitude Movement'),
              filter = 'top',
              rownames = FALSE,
              extensions = 'Buttons',
              options = list(dom = 'Blfrtip',
                             buttons = c('csvHtml5', 'excelHtml5'),
                             pageLength = 10,
                             lengthMenu = c(10, 100, 1000)))
```

# Slide 3 & 4 (Car Specifications) {#MPGTable data-icon='fa-car' data-navmenu='Tables'}

``` {r}
DT::datatable(data = mpg,
              colnames = c('Manufacturer', 'Model', 'Displacement', 'Year', 'Cylinders', 'Transmission', 'Drive', 'City MPG', 'Hwy MPG', 'Fuel', 'Class'),
              filter = 'top',
              rownames = FALSE,
              extensions = 'Buttons',
              options = list(dom = 'Blfrtip',
                             buttons = c('csvHtml5', 'excelHtml5'),
                             pageLength = 10,
                             lengthMenu = c(10, 100, 1000)))
```







